---
title: "Player Transfers"
author: "Rishabh Kumar"
date: "2022"
output:
  html_document:
    theme:
      bootswatch: cyborg
  pdf_document: default
---

**This is a description of the data: **
The dataset deals with soccer players. This dataset deals with transfers for these soccer players. In general, these international leagues have a lot of transfers and generally these transfers are associated with a lot of fees. Therefore it is very essential to price these players correctly. There is a lot of back and forth in these transfers and these are a success or failure based on the initial evaluation of the player. The scope of this project would be to build a prediction model which can assess the transfer value of a player.
The dataset here consists of a lot of valuable information essential for evaluating the cost of a player. There are a total of 43 attributes in this dataset.

**Some of the attributes in this dataset are: **
1. Market Value
2. Price of transfer (Continuous Integer)
3. Acceleration (Continuous Integer)
4. Age (Continuous Integer)
5. Aggresion (Continuous Integer)
6. Agility (Continuous Integer)
7. Att. Position (Continuous Integer)
8. Name (Index Variable)
9. Ball Control (Continuous Integer)
10. Birth Date (Continuous Integer)
11. Birth Place (Nominal Categorical)
12. Posistion (Nominal Categorical)
13. Version (Ordinal Categorical)
14. Dribbling (Continuous Integer)
15. Finishing (Continuous Integer)
16. Strength (Continuous Integer)
17. Speed (Continuous Integer)

**Original Format: **
The original format of this dataset was a .txt file. It had to be converted into a .csv file so that it can be viewed in the correct format as well as ingested by R and can be used to build a predictive model.

```{r, echo = TRUE}
# This chunk of the document is for loading the dataset. 
# I will be using the read_table function to read data into a dataframe
# as.data.frame converts the table into a dataframe
fifadata=as.data.frame(read.table("./baseNormalizada.txt",sep="\t", header=TRUE))
```

```{r, echo = TRUE}
# Cleaning dataset. Removing some columns as well as changing date format columns
library(janitor)
# Formatting date column
fifadata$Birth.Date <- as.Date(as.character(fifadata$Birth.Date),format = "%d/%m/%y")

# Removing constant columns since no added value in machine learning algorithms
fifadata=remove_constant(fifadata)

# Dropping a few columns
fifadata <- subset(fifadata, select = -c(GK.Diving, GK.Handling,GK.Kicking,GK.Positioning))
```



This dataframe has `r nrow(fifadata)` and `r nrow(fifadata)`. The names of the columns and a brief description of each are in the table below:

| ColumnName | Description |
| :---------- | :---------- |
| Price | Shows the price of a player |
| Market Value | Shows the market value of a player according to FIFA |
| Acceleration | 0-100 value with direct correlation to price |
| Age | Shows age. 22-29 is when the price is highest for a player |
| Aggression | 0-100 value showing aggression |
| Agility | 0-100 value showing agility |
| Balance | 0-100 value showing balance |
| Personal trait columns | More columns like Balance, Ball control, Speed, Crossing, Finishing, Heading, Height, Long Pass, Short Pass, Tackle, Vision etc. |
| Position | Shows where the player is playing as a soccer player |
| Preferred Foot | Whether the player is left footed or right footed |
| Name | Indicates who the player is and acts like an index |
| Game Edition | Which FIFA edition gives the price and personal traits |
| Birth Place | Where the player was born is essential for his/her price |

```{r, echo=TRUE}
# Summarizing data
subfifa=fifadata[,c("Price","Age","Weight")]

NAcounts=c(sum(is.na(subfifa$Price)),sum(is.na(subfifa$Age)),sum(is.na(subfifa$Weight)))
smry=do.call(cbind, lapply(subfifa, summary))
smry = rbind(smry,NAcounts)
smry=smry[c("Mean","Max.","Min.","NAcounts"),]
knitr::kable(smry, format="html")
```

